Structuring College Access

### 2025-03-15 index.qmd
small changes to comd

- Geomarkets carve states and metro areas into smaller geographic regions meant to define local recruiting markets [@RN4982]

@@

- Predicts how demand for a college varies by Geomarket, based on characteristics of households in Geomarket
- Categorize students into 4 market segments -- local, in-state, regional, national -- based on SAT score-sending behavior
  - local: send most scores to colleges within Geomarket
  - regional: send most scores out-of-state but in-region (e.g., Midwest)
- "Good" colleges should look for regional and national students
  - Like @RN2247, except College Board creates product from it
  - @RN4982 create outputs that become EPS software

### Scholarship on Quantification {.hide}
#### Discussions of correlation and homophily by @RN4975[chapter 1]

@@

- Student lists purchased by 14 public universities from 2016-2020
  - 414 student lists associated with 2.5 million prospects
    - Data: search filter criteria; and de-identified student-level data
    - Each prospect has a home and a HS zip code (point geoms)
- Analyze purchases that include all Geomarkets in a metro area
  - Show who included/excluded if we filter on particular Geomarkets

>>>>

- Geomarkets carve states and metro areas into smaller geographic regions

@@

- Predicts how demand for a college varies by Geomarket, based on characteristics of households in Geomarket
- Categorize students into 4 market segments -- local, in-state, regional, national -- based on SAT score-sending behavior
  - local: send most scores to colleges within Geomarket
  - regional: send most scores out-of-state but in-region (e.g., Midwest)
- Selective colleges should look for regional and national students
- @RN4982 create outputs that become EPS software

<!--   - Like @RN2247, except College Board creates product from it -->

### Scholarship on Quantification {.hide}
#### Discussions of correlation and homophily by @RN4975

@@

- Student lists purchased by 14 public universities from 2016-2020
  - 414 student lists associated with 2.5 million prospects
    - Data: search filter criteria; and de-identified student-level data
    - Each prospect has home and HS zip code (point geometry)
- Analyze purchases that include all Geomarkets in a metro area
  - Show who included/excluded if we filter on particular Geomarkets
